The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2018-06-06 Paper/jaccardbaetica.tex
modify some error

From the database, we collected the site where it was found and the stamp code. We also created a new column with the area where stamps were found. These areas, known as \textit{conventus}, were administrative centers for territorial organization in the Roman Empire. Dressel 20 stamps were found in three different \textit{conventus}: \textit{Hispalis} (currently Seville), \textit{Corduba} (currently C\'ordoba) and \textit{Astigi} (currently Écija, Sevilla) \citep{rodriguez_economioleicola_1977,chic_datos_2001,berni_millet_epigrafianforica_2008} .

@@

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/frequency}
\caption{Dendrogram obtained by Morisita-Horn algorithm of different amphora workshops in Baetica area. Colors are represented by areas divided into Hispalis (red), Astigi (green) and Corduba (blue).}
\label{frequency}
\end{figure} 
%explicar por qué: mayor intensifación en las excavaciones quizás en sevilla

@@

In our analysis, no strong relation between stamps and geographic distance were detected in amphora workshops. Indeed, the analysis suggests that there is not connection between stamps and the same amphora workshops, excluding certain exceptions when nearby workshops share the same amphoric stamps. Consequently the majority of stamps are located in different amphora workshops and only similar stamps between closer amphora workshops were found. In any case, our results show that most similar stamps were detected in the same conventus area. These stamps tend to share the same area of production but there is not a general relation between groups of amphora workshops and area.

The hypothesis about groups of amphora workshops sharing the same stamps seems do not match with the results of the analysis even though there are similar stamps in closer workshops. Rather, it seems that each workshop were organized independently with different stamps. Those stamps detected in closer workshops do not move from other farthest workshops. In other words, the stamps tend to keep in the same area and different stamps were located in a same amphora workshops. 
This could be defined by several factors. Firstly, each workshop had a different organization involved to the use of stamps and they were not used in other workshops. Secondly, stamps similarity in closer workshops could be linked to a spatial pattern. It is more probably than closer workshops tend to share more traits than farthest. While the role of river was significant for the distribution of amphorae in consumption places, river connection amongst workshops was not relevant for the distribution of stamps. Finally, the distribution of stamps could have showed some research bias. In some cases, workshops have been catalogued with different names despite belonging to the same workshops or being closer between each other. Additionally, most workshops were not widely excavated.

>>>>

From the database, we collected the site where it was found and the stamp code. We also created a new column with the area where stamps were found. These areas, known as \textit{conventus}, were administrative centers for territorial organization in the Roman Empire. Dressel 20 stamps were found in three different \textit{conventus}: \textit{Hispalensis} (currently Seville, hereafter Hispalis), \textit{Cordubensis} (currently C\'ordoba, hereafter Corduba) and \textit{Astigi} (currently Écija, Sevilla, hereafter Astigi) \citep{rodriguez_economioleicola_1977,chic_datos_2001,berni_millet_epigrafianforica_2008} .

@@

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/frequency}
\caption{Distribution of the number of stamps for each area. Colors are represented by areas divided into Hispalis (red), Astigi (green) and Corduba (blue).}
\label{frequency}
\end{figure} 
%explicar por qué: mayor intensifación en las excavaciones quizás en sevilla

@@

In our analysis, no strong relation between stamps and geographic distance were detected in amphora workshops. Indeed, the analysis suggests that there is not connection between stamps and the same amphora workshops, excluding certain exceptions when nearby workshops share the same amphoric stamps. Consequently the majority of stamps are located in different amphora workshops and only similar stamps between closer amphora workshops were found. In any case, our results show that most similar stamps were detected in the same \textit{conventus} area. These stamps tend to share the same area of production but there is not a general relation between groups of amphora workshops and area.

The hypothesis about groups of amphora workshops sharing the same stamps seems do not match with the results of the analysis even though there are similar stamps in closer workshops. Rather, it seems that each workshop were organized independently with different stamps. Those stamps detected in closer workshops do not move from other farthest workshops. In other words, the stamps tend to keep in the same area and different stamps were located in a same amphora workshops. 
This could be defined by several factors. Firstly, each workshop had a different organization involved to the use of stamps and they were not used in other workshops. Secondly, stamps similarity in closer workshops could be linked to a spatial pattern. It is more probably than closer workshops tend to share more traits than farthest. While the role of river was significant for the distribution of amphorae in consumption places, river connection amongst workshops was not relevant for the distribution of stamps. Finally, the distribution of stamps could have showed some research bias. In some cases, workshops have been catalogued with different names despite belonging to the same workshops or being closer between each other. Additionally, most of the workshops were not widely excavated.
